Enhancement of SDR in Thessaloniki

### 2024-03-28 GHI_enh_04_investigate.tex
Commit 2024-03-28 11:10

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-03-24}

@@

Arima: -0.013183 +/- 6.904159

@@

@@

Arima: 33.721354 +/- 8.881459

@@

Arima: -0.013183 +/- 6.904159

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

\begin{verbatim}
2024-03-24 18:26:30.5 athan@tyler GHI_enh_04_investigate.R 2.229609 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-03-28}

@@

Arima: -0.013183 +/- 6.898051

@@

Units for GLB\_diff.p\_10 : Watt/m\^{}2

lmD: 1.034078 +/- 0.239285

lmY: 1.034088 +/- 0.23929

Arima: 1.03413 +/- 0.363494

Units for GLB\_diff.p\_5 : Watt/m\^{}2

lmD: 0.944568 +/- 0.252832

lmY: 0.944578 +/- 0.252837

Arima: 0.944623 +/- 0.38704

Units for GLB\_diff.p\_90 : Watt/m\^{}2

lmD: 1.109672 +/- 0.07725

lmY: 1.109686 +/- 0.077252

Arima: 1.109689 +/- 0.115906

Units for GLB\_diff.p\_95 : Watt/m\^{}2

lmD: 1.167512 +/- 0.073583

lmY: 1.167525 +/- 0.073584

Arima: 1.167532 +/- 0.106265

@@

Arima: 33.721354 +/- 8.881986

@@

Arima: -0.013183 +/- 6.898051

Units for GLB\_ench.p\_10 : Watt/m\^{}2

lmD: 0.00184 +/- 0.000301

lmY: 0.00184 +/- 0.000301

Arima: 0.00184 +/- 0.000473

Units for GLB\_ench.p\_5 : Watt/m\^{}2

lmD: 0.001768 +/- 0.000292

lmY: 0.001768 +/- 0.000292

Arima: 0.001768 +/- 0.000451

Units for GLB\_ench.p\_90 : Watt/m\^{}2

lmD: 0.002432 +/- 0.000235

lmY: 0.002432 +/- 0.000235

Arima: 0.002432 +/- 0.000369

Units for GLB\_ench.p\_95 : Watt/m\^{}2

lmD: 0.002624 +/- 0.000229

lmY: 0.002624 +/- 0.000229

Arima: 0.002624 +/- 0.000346

@@

Units for GLB\_diff.p\_10 : Watt/m\^{}2

lmD: -0.00734 +/- 0.019077

lmY: -0.007339 +/- 0.019077

Arima: -0.007339 +/- 0.019267

Units for GLB\_diff.p\_5 : Watt/m\^{}2

lmD: -0.027816 +/- 0.017696

lmY: -0.027816 +/- 0.017696

Arima: -0.027816 +/- 0.017858

Units for GLB\_diff.p\_90 : Watt/m\^{}2

lmD: 0.49203 +/- 0.073274

lmY: 0.492037 +/- 0.073275

Arima: 0.492032 +/- 0.081403

Units for GLB\_diff.p\_95 : Watt/m\^{}2

lmD: 0.595557 +/- 0.083417

lmY: 0.595566 +/- 0.083419

Arima: 0.59556 +/- 0.094857

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-31} \end{center}

Units for GLB\_ench.p\_10 : Watt/m\^{}2

lmD: 2.1e-05 +/- 3.2e-05

lmY: 2.1e-05 +/- 3.2e-05

Arima: 2.1e-05 +/- 3.6e-05

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-32} \end{center}

Units for GLB\_ench.p\_5 : Watt/m\^{}2

lmD: -1.2e-05 +/- 2.9e-05

lmY: -1.2e-05 +/- 2.9e-05

Arima: -1.2e-05 +/- 3.4e-05

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-33} \end{center}

Units for GLB\_ench.p\_90 : Watt/m\^{}2

lmD: 0.000922 +/- 0.000106

lmY: 0.000922 +/- 0.000106

Arima: 0.000922 +/- 0.00012

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-34} \end{center}

Units for GLB\_ench.p\_95 : Watt/m\^{}2

lmD: 0.001074 +/- 0.000117

lmY: 0.001074 +/- 0.000117

Arima: 0.001074 +/- 0.000134

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-35} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-36} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-37} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-38} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-39} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-40} \end{center}

Units for GLB\_diff.p\_10 : Watt/m\^{}2

lmD: -0.069532 +/- 0.179279

lmY: -0.06952 +/- 0.179282

Arima: -0.124647 +/- 0.339466

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-41} \end{center}

Units for GLB\_diff.p\_5 : Watt/m\^{}2

lmD: -0.089703 +/- 0.178956

lmY: -0.089692 +/- 0.178959

Arima: -0.144328 +/- 0.338161

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-42} \end{center}

Units for GLB\_diff.p\_90 : Watt/m\^{}2

lmD: 0.16704 +/- 0.22968

lmY: 0.167077 +/- 0.229683

Arima: 0.146398 +/- 0.353614

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-43} \end{center}

Units for GLB\_diff.p\_95 : Watt/m\^{}2

lmD: 0.17703 +/- 0.238162

lmY: 0.177067 +/- 0.238165

Arima: 0.158966 +/- 0.358093

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-44} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-45} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-46} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-47} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-48} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-49} \end{center}

Units for GLB\_ench.p\_10 : Watt/m\^{}2

lmD: 0.000168 +/- 0.000199

lmY: 0.000168 +/- 0.000199

Arima: 0.000157 +/- 0.000257

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-50} \end{center}

Units for GLB\_ench.p\_5 : Watt/m\^{}2

lmD: 0.000155 +/- 0.000199

lmY: 0.000155 +/- 0.000199

Arima: 0.000144 +/- 0.000256

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-51} \end{center}

Units for GLB\_ench.p\_90 : Watt/m\^{}2

lmD: 0.000509 +/- 0.000261

lmY: 0.000509 +/- 0.000261

Arima: 0.000508 +/- 3e-04

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-52} \end{center}

Units for GLB\_ench.p\_95 : Watt/m\^{}2

lmD: 0.00051 +/- 0.00027

lmY: 0.00051 +/- 0.00027

Arima: 0.000509 +/- 0.000307

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-53} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/daily-54} \end{center}

@@

\begin{verbatim}
2024-03-28 08:59:32.3 athan@sagan GHI_enh_04_investigate.R 0.815632 mins
\end{verbatim}
